---
title: "examp function"
author: "HC"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{examp function}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview
__examp__ is a simple R package including two functions. _Bobble_ is a simple function developed to sort the given array of values.  _fac_ is a function developed to calculate the factorial. _fcount_ , _fEcount_ , _fE2count_ ,are three different kernel functions.
## Benchmarking _Bobble_ and _fac_

The source R code for _Bobble_ is as follows:
```{r}
Bobble<-function(L,n){
 library(Rcpp)
  cppFunction('NumericMatrix Bobble(NumericMatrix x,int m){
  NumericMatrix mat(m, 1);
  NumericMatrix Index(m,1);
  for (int k=0;k<m;k++){
    mat(k,0)=x(k,0);
    Index(k,0)=k+1;
  }
  int i,j,t;
  double l;
  for(i=0;i<(m-1);i++){
     for(j=0;j<(m-1-i);j++){
        if(mat(j,0)>mat((j+1),0)){
        l=mat(j,0);mat(j,0)=mat((j+1),0);mat((j+1),0)=l;
        t=Index(j,0);Index(j,0)=Index((j+1),0);Index((j+1),0)=t;
        }}}
  return(Index);
}')
LL<-numeric(n)
Ind<-Bobble(L,n)
return(Ind)
}
```
This function aims  to sort the given array of values.

Here is the example:
```{r}
Bobble<-function(L,n){
  library(Rcpp)
  cppFunction('NumericMatrix Bobble(NumericMatrix x,int m){
  NumericMatrix mat(m, 1);
  NumericMatrix Index(m,1);
  for (int k=0;k<m;k++){
    mat(k,0)=x(k,0);
    Index(k,0)=k+1;
  }
  int i,j,t;
  double l;
  for(i=0;i<(m-1);i++){
     for(j=0;j<(m-1-i);j++){
        if(mat(j,0)>mat((j+1),0)){
        l=mat(j,0);mat(j,0)=mat((j+1),0);mat((j+1),0)=l;
        t=Index(j,0);Index(j,0)=Index((j+1),0);Index((j+1),0)=t;
        }}}
  return(Index);
}')
LL<-numeric(n)
Ind<-Bobble(L,n)
return(Ind)
}
L<-matrix(rnorm(20,1,4),nrow=20)
n<-20
LL<-numeric(n)
Ind<-Bobble(L,n)
Res<-numeric(n)
for ( k in(1:n)){
  ids<-Ind[k]
  Res[k]<-L[ids]
  LL[k]<-L[k,1]
}
print("the original order is:\n")
print(LL)
print("the sorted order is:\n")
print(Res)
```

The source R code for _fac_ is as follows: 
```{r}
fac<-function(n){
library(Rcpp)
cppFunction('int fac(int m){
  int P;
  if((m==0)||(m==1)){
    P=1;
  }
  else {P=m*fac(m-1);}
  
  return(P);
}')

y<-fac(n)

return(y)
}
```
This function aims to calculate the factorial.

Here is the example:
```{r}
fac<-function(n){
requireNamespace('Rcpp', quietly = TRUE)
cppFunction('int fac(int m){
  int P;
  if((m==0)||(m==1)){
    P=1;
  }
  else {P=m*fac(m-1);}
  
  return(P);
}')

y<-fac(n)

return(y)
}

n<-fac(5)
print(n)
```


The source R code for _fcount_ is as follows: 
```{r}
fcount<-function(a1,a2,b1,b2,ha,hb){#Multiplicative kernel
  s<-0
  bar1<-(b1-a1)/ha
  bar2<-(b2-a2)/hb
  bar<-((-1<=bar1)&(bar1<1)&(-1<=bar2)&(bar2<1))
  if (bar){s<-1}
  return(s/(ha*hb))
}
```
Here is the example:
```{r}
fcount<-function(a1,a2,b1,b2,ha,hb){#Multiplicative kernel
  s<-0
  bar1<-(b1-a1)/ha
  bar2<-(b2-a2)/hb
  bar<-((-1<=bar1)&(bar1<1)&(-1<=bar2)&(bar2<1))
  if (bar){s<-1}
  return(s/(ha*hb))
}

 library(ks)
 library(rgl)
 xx <- as.matrix(faithful)
 kdex <- kde(xx)
 data("faithful")
 ef<-faithful$eruptions
 wf<-faithful$waiting
 h1<-0.3
 h2<-6
 x<-unlist(kdex$eval.points[1])
 y<-unlist(kdex$eval.points[2])
 n<-length(ef)
 n1<-length(x)
 n2<-length(y)
 z1<-matrix(rep(0,n1*n2),nrow=n1)
 for ( i in 1:n1){
   for (j in 1:n2){
     k1<-0
     for (l in 1:n){
       k1<-k1+fcount(ef[l],wf[l],x[i],y[j],h1,h2)
     }
     z1[i,j]<-k1/n
   }
 }
 persp(x, y, z1,phi = 30, theta = 40, col = 'black', border = 0
       ,xlab='eruptions',ylab='waiting'
       ,main='Results under Multiplicative kernel')
```

The source R code for _fEcount_ is as follows: 
```{r}
fEcount<-function(a1,a2,b1,b2,ha,hb){#The multivariate Epanechnikov (spherical)
  s<-0
  bar1<-(b1-a1)/ha
  bar2<-(b2-a2)/hb
  bar3<-c(bar1,bar2)
  bar<-t(bar3)%*%(bar3)
  if(bar<=1){
    s<-(1-bar)
  }
  return(s/(ha*hb))
}
```

Here is the example:
```{r}
fEcount<-function(a1,a2,b1,b2,ha,hb){#The multivariate Epanechnikov (spherical)
  s<-0
  bar1<-(b1-a1)/ha
  bar2<-(b2-a2)/hb
  bar3<-c(bar1,bar2)
  bar<-t(bar3)%*%(bar3)
  if(bar<=1){
    s<-(1-bar)
  }
  return(s/(ha*hb))
}

 library(ks)
 library(rgl)
 xx <- as.matrix(faithful)
 kdex <- kde(xx)
 data("faithful")
 ef<-faithful$eruptions
 wf<-faithful$waiting
 h1<-0.3
 h2<-6
 x<-unlist(kdex$eval.points[1])
 y<-unlist(kdex$eval.points[2])
 n<-length(ef)
 n1<-length(x)
 n2<-length(y)
 z2<-matrix(rep(0,n1*n2),nrow=n1)
 for ( i in 1:n1){
   for (j in 1:n2){
     k2<-0
     for (l in 1:n){
       k2<-k2+fEcount(ef[l],wf[l],x[i],y[j],h1,h2)
     }
     z2[i,j]<-k2/n
   }
 }
 persp(x, y, z2,phi = 30, theta = 40, col = 'red', border = 0,
     xlab='eruptions',ylab='waiting'
       ,main='Results under  Multivariate Epanechnikov (spherical)')
```



The source R code for _fE2count_ is as follows: 
```{r}
fE2count<-function(a1,a2,b1,b2,ha,hb){#The multivariate Epanechnikov (multiplicative)
  s<-0
  bar1<-(b1-a1)/ha
  bar2<-(b2-a2)/hb
  bar<-((abs(bar1)<=1)&(abs(bar2)<=1))
  if (bar){
    s<-(3/4)^2*(1-(bar1)^2)*(1-(bar2)^2)
  }
  return(s/(ha*hb))
}
```



Here is the example:
  
```{r}
fE2count<-function(a1,a2,b1,b2,ha,hb){#The multivariate Epanechnikov (multiplicative)
  s<-0
  bar1<-(b1-a1)/ha
  bar2<-(b2-a2)/hb
  bar<-((abs(bar1)<=1)&(abs(bar2)<=1))
  if (bar){
    s<-(3/4)^2*(1-(bar1)^2)*(1-(bar2)^2)
  }
  return(s/(ha*hb))
}

library(ks)
library(rgl)
xx <- as.matrix(faithful)
kdex <- kde(xx)
data("faithful")
ef<-faithful$eruptions
wf<-faithful$waiting
h1<-0.3
h2<-6
x<-unlist(kdex$eval.points[1])
y<-unlist(kdex$eval.points[2])
n<-length(ef)
n1<-length(x)
n2<-length(y)
z3<-matrix(rep(0,n1*n2),nrow=n1)
for ( i in 1:n1){
   for (j in 1:n2){
     k3<-0
     for (l in 1:n){
       k3<-k3+fE2count(ef[l],wf[l],x[i],y[j],h1,h2)
     }
    z3[i,j]<-k3/n
   }
}
persp(x, y, z3,phi = 30, theta = 40, col = 'blue', border = 0
       ,xlab='eruptions',ylab='waiting'
       ,main='Results under  Multivariate Epanechnikov (multiplicative)')
```
